Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-24 paper.tex
addressing some comments + removing others + SoA-first-paragraph

%***TO DO***: complete this considering the new contents and results\\
% Instead of just writing this you should say what has changed and
% what should be changed. For instance, the paragraph below probably
% shouldn't - JJ 
Publishing a book, in the same way as releasing any other cultural product with a
physical substrate, implies several
types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution and storage processes; most of these costs are associated
to the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new 
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
%which should be obvious from the get go, don't know why you need 4
%papers to affirm that - JJ
%please someone address this - JJ

@@

The problem is specially acute for book publishers, who, among other
content providers, release new {\em products} more frequently than
other industries, so that they face the 
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
% Antonio - 'sunk inventory cost' es corecto?
% Sí, pero corecto no lo es. - JJ
whereas if the number of printed copies was not enough, a new print
run can be made, resulting in temporary losses due to lack of supply;
a real problem, to be sure, but less dire than having too many unsold
books.  
%FERGU: el you ese es muy coloquial, reescribir
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
% Corregido - JJ
In this sense, errors in one or the other direction do not have the same impact.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
%FERGU: lo de one or the other direction creo que confunde
% Lo que habría que decir es hablar de cómo hemos tratado una u otra
% cosa. ¿Estamos sesgando hacia predecir menos ventas de las que
% habría? ¿O simplemente es por tener un poco de background? Igual
% deberíamos haberlas tratado de forma diferente. - JJ

@@

% [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
%  por eso quiero comenzar hablando de la aplicación de métodos
%  de predicción en la industria en general, que sí hay bastante bibliografía.
% Antonio - me parece bien

% Antonio - Cosas generales a mejorar en el SotA:
% - habría que comparar más veces este trabajo con lo que hacen otros, destacando nuestras diferencias. Sólo se menciona al final de la sección
% - habría que destacar claramente ls aportes de este trabajo al SotA, cómo hace que avance ;)
% - habría que incluir citas a artículos de la revista que elijamos y comentarlos aquí

% Sales forecasting is a problem which has been addressed several times
% in the literature.
% This sentence is useless
In the past, sales prediction has been performed using methods such as  regression models
\cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy 
systems \cite{Mastorocostas2001}, applied to different industrial
sectors. 
% ¿Y qué? Esta frase
% no aporta nada. La primera frase
% tiene que enmarcar el estado del
% arte - JJ
% Antonio - la he intentado mejorar.
% Muchas cosas de la intro tendrían que venir aquí, al estado del
% arte. Habría que reescribir la intro. - JJ
% ¿Qué usan esos métodos? - JJ

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production (how many books should be printed when a new
book is published). 
%FERGU: quitad los paréntesis :)
% Fergu: quítalos tú, tío, aquí puede editar todo el mundo - JJ
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

>>>>

Publishing a book, in the same way as releasing any other cultural product with a
physical substrate, implies several types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution and storage processes; most of these costs are associated
to the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new product is extremely important, so 
that production runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}.

@@

The problem is specially acute for book publishers, who, among other
content providers, release new {\em products} more frequently than
other industries, so that they face the 
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can be made, resulting in temporary losses due to lack of supply;
a real problem, to be sure, but less dire than having too many unsold
books.  
%FERGU: el you ese es muy coloquial, reescribir
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
% Corregido - JJ
In this sense, errors in one or the other direction do not have the same impact.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
%FERGU: lo de one or the other direction creo que confunde
% Lo que habría que decir es hablar de cómo hemos tratado una u otra
% cosa. ¿Estamos sesgando hacia predecir menos ventas de las que
% habría? ¿O simplemente es por tener un poco de background? Igual
% deberíamos haberlas tratado de forma diferente. - JJ

@@

As far as we know, no previous attempt can be found in the literature in which 
prediction methods have been applied to estimate the print run. 
However, similar techniques to those proposed in this paper, e.g. 
regression models \cite{Papalexopoulos1990}, 
neural networks \cite{Yoo1999} 
or fuzzy systems \cite{Mastorocostas2001}, 
have been applied to solve sales prediction problems in other industrial sectors.

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production, i.e. how many books should be printed when a new
book is published. 
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?
